### 2024-01-12 inst/scripts/exploreNeutralTraits.Rmd
Change naming of a few function and update documentation correspondantly

```{r}
z=4
neutraltraitsParam=initNeutralTraitsPathways(z = z)
neutraltraitsParam$post[,"i"]=1
neutraltraitsParam$s=rep(.5,z)
traitsid=paste0("t",1:z)
```

@@

Age of people is initially random
```{r randompop}
communities=unlist(lapply(seq_along(initcomus$size),function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(n=sum(initcomus$size),age="random",community = communities),initNeutralTraits(sum(initcomus$size),z))
```

@@

```
```{r}
devtools::load_all(".")
z=4
neutraltraitsParam=initNeutralTraitsPathways(z = z)
neutraltraitsParam$post[,"i"]=1
neutraltraitsParam$s=c(0,1)
traitsid=paste0("t",1:z)
km=0
ki=z
G=2
initcomus=initialiseCommunities(traits=initAdaptiveTraits(ki=3,km=1,n=3),coordinates=random2Dgrid(K=ki+km,Gx=G),G=G,sizes=150,plot=T)
communities=unlist(lapply(seq_along(initcomus$size),function(i)rep(i,initcomus$size[i])))
data(population)
population[,traitsid]=0
for(i in 1:z){population[population[,"community"]==i,traitsid[i]]=1}
knitr::kable(aggregate(population[,traitsid],by=list(population[,"community"]),sum))
tstep=200
rhos=c(0,1)
repli=10
rhodepSBBIB=lapply(rhos,function(rho){
           neutraltraitsParam$post[,]=0
           neutraltraitsParam$pre[,]=0
           neutraltraitsParam$post[,"i"]=1
           allinlaw=parSapply(cl,1:repli,function(r)
                              {
                                  set.seed(as.numeric(Sys.time())+r)
                                  quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.02, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                  pop=quickV$population
                                  do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)
           neutraltraitsParam$post[,"i"]=0
           neutraltraitsParam$post[,"h"]=1
           allposthoriz=parSapply(cl,1:repli,function(r){
                                  set.seed(as.numeric(Sys.time())+r)
                                      quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time","visu"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL,beta=0)
                                      pop=quickV$population
                                     do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

>>>>

```{r}
z=4
neutraltraitsParam=generatePathways(z = z)
neutraltraitsParam$post[,"i"]=1
neutraltraitsParam$s=rep(.5,z)
traitsid=paste0("t",1:z)
```

@@

Age of people is initially random
```{r randompop}
communities=unlist(lapply(seq_along(initcomus$size),function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(n=sum(initcomus$size),age="random",community = communities),generateTraitsMatrix(sum(initcomus$size),z))
```

@@

```
```{r}
devtools::load_all(".")
z=4
neutraltraitsParam=generatePathways(z = z)
neutraltraitsParam$post[,"i"]=1
neutraltraitsParam$s=c(0,1)
traitsid=paste0("t",1:z)
km=0
ki=z
G=2
initcomus=initialiseCommunities(traits=initAdaptiveTraits(ki=3,km=1,n=3),coordinates=random2Dgrid(K=ki+km,Gx=G),G=G,sizes=150,plot=T)
communities=unlist(lapply(seq_along(initcomus$size),function(i)rep(i,initcomus$size[i])))
data(population)
population[,traitsid]=0
for(i in 1:z){population[population[,"community"]==i,traitsid[i]]=1}
knitr::kable(aggregate(population[,traitsid],by=list(population[,"community"]),sum))
tstep=200
rhos=c(0,1)
repli=10
rhodepSBBIB=lapply(rhos,function(rho){
           neutraltraitsParam$post[,]=0
           neutraltraitsParam$pre[,]=0
           neutraltraitsParam$post[,"i"]=1
           allinlaw=parSapply(cl,1:repli,function(r)
                              {
                                  set.seed(as.numeric(Sys.time())+r)
                                  quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.02, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                  pop=quickV$population
                                  do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)
           neutraltraitsParam$post[,"i"]=0
           neutraltraitsParam$post[,"h"]=1
           allposthoriz=parSapply(cl,1:repli,function(r){
                                  set.seed(as.numeric(Sys.time())+r)
                                      quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time","visu"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL,beta=0)
                                      pop=quickV$population
                                     do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

### 2024-01-12 inst/scripts/testDemo.Rmd
Change naming of a few function and update documentation correspondantly

a=initAdaptiveTraits(ki=ki,km=km)
z=4 #number of neutral traits
neutraltraitsParam=initNeutralTraitsPathways(z = z)
neutraltraitsParam$s=c(0,0,1,1)

ip=1:N
names(ip)=ip
population=lapply(ip,function(i) list( id=as.character(i), traits=sample(c(0,1),size=z,replace=T), age=sample.int(endrepro-5,1), community=sample.int(K,1), sex=sample(c("F","M"),1), repro=FALSE, partner=-1))
                                      population=cbind(newpop(N,age="random",community = communities),initNeutralTraits(N,z))

@@

```{r}
library(parallel)
m=1
b=0.2
r=0.05
tstep=300
d=0.001
N=200
ip=1:N
names(ip)=ip
z=4 #number of neutral traits
neutraltraitsParam=initNeutralTraitsPathways(z = z)
neutraltraitsParam$s=c(0,0,1,1)
population=lapply(ip,function(i) list( id=as.character(i), traits=sample(c(0,1),size=z,replace=T), age=sample.int(65,1), community=1, sex=sample(c("F","M"),1), repro=FALSE, partner=-1))

@@

```{r}
m=1
b=0.2
r=0.05
tstep=300
d=0.001
N=200
ip=1:N
names(ip)=ip
z=4 #number of neutral traits
neutraltraitsParam=initNeutralTraitsPathways(z = z)
neutraltraitsParam$s=c(0,0,1,1)
population=lapply(ip,function(i) list( id=as.character(i), traits=sample(c(0,1),size=z,replace=T), age=sample.int(65,1), community=1, sex=sample(c("F","M"),1), repro=FALSE, partner=-1))

neutraltraitsParam=initNeutralTraitsPathways(z = 2)
traitsid=paste0("t",1:2)
percomu=50
K=2
km=0
ki=2
N=100
pos=random2Dgrid(K=K,Gx=2)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=2,plot=T,sizes=c(50,50))
communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(N,age="random",community = communities),initNeutralTraits(N,z))
quickV=modelVector(K=K, m=1, b=0.1, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=1000, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","deaths","popsize"),logging=c("time","visu"),ma=1,traitsid=paste0("t",1:z))

@@

neutraltraitsParam=initNeutralTraitsPathways(z = 2)
traitsid=paste0("t",1:2)
percomu=50
K=2
km=0
ki=2
N=100
pos=random2Dgrid(K=K,Gx=5)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=5,plot=T,sizes=c(50,50))
communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(N,age="random",community = communities),initNeutralTraits(N,z))
initcomus$size=unname(table(smallpop[,"community"]))
multrep=replicate(10,modelVector(K=K, m=1, b=0.39, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=smallpop, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","deaths","popsize","popfull","repros","births"),logging=c("time","fission"),ma=1,traitsid=paste0("t",1:z),F_Th=180))

>>>>

a=initAdaptiveTraits(ki=ki,km=km)
z=4 #number of neutral traits
neutraltraitsParam=generatePathways(z = z)
neutraltraitsParam$s=c(0,0,1,1)

ip=1:N
names(ip)=ip
population=lapply(ip,function(i) list( id=as.character(i), traits=sample(c(0,1),size=z,replace=T), age=sample.int(endrepro-5,1), community=sample.int(K,1), sex=sample(c("F","M"),1), repro=FALSE, partner=-1))
                                      population=cbind(newpop(N,age="random",community = communities),generateTraitsMatrix(N,z))

@@

```{r}
library(parallel)
m=1
b=0.2
r=0.05
tstep=300
d=0.001
N=200
ip=1:N
names(ip)=ip
z=4 #number of neutral traits
neutraltraitsParam=generatePathways(z = z)
neutraltraitsParam$s=c(0,0,1,1)
population=lapply(ip,function(i) list( id=as.character(i), traits=sample(c(0,1),size=z,replace=T), age=sample.int(65,1), community=1, sex=sample(c("F","M"),1), repro=FALSE, partner=-1))

@@

```{r}
m=1
b=0.2
r=0.05
tstep=300
d=0.001
N=200
ip=1:N
names(ip)=ip
z=4 #number of neutral traits
neutraltraitsParam=generatePathways(z = z)
neutraltraitsParam$s=c(0,0,1,1)
population=lapply(ip,function(i) list( id=as.character(i), traits=sample(c(0,1),size=z,replace=T), age=sample.int(65,1), community=1, sex=sample(c("F","M"),1), repro=FALSE, partner=-1))

neutraltraitsParam=generatePathways(z = 2)
traitsid=paste0("t",1:2)
percomu=50
K=2
km=0
ki=2
N=100
pos=random2Dgrid(K=K,Gx=2)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=2,plot=T,sizes=c(50,50))
communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(N,age="random",community = communities),generateTraitsMatrix(N,z))
quickV=modelVector(K=K, m=1, b=0.1, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=1000, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","deaths","popsize"),logging=c("time","visu"),ma=1,traitsid=paste0("t",1:z))

@@

neutraltraitsParam=generatePathways(z = 2)
traitsid=paste0("t",1:2)
percomu=50
K=2
km=0
ki=2
N=100
pos=random2Dgrid(K=K,Gx=5)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=5,plot=T,sizes=c(50,50))
communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(N,age="random",community = communities),generateTraitsMatrix(N,z))
initcomus$size=unname(table(smallpop[,"community"]))
multrep=replicate(10,modelVector(K=K, m=1, b=0.39, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=smallpop, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","deaths","popsize","popfull","repros","births"),logging=c("time","fission"),ma=1,traitsid=paste0("t",1:z),F_Th=180))
